### 2019-03-11 response/response-demography-1.tex

- complete rewrite of introduction
- highlight how method is different in ``Estimation Strategy'' section.

Second, a conceptual framework or theoretical argument is needed to
motivate the decision to examine birth intervals and sex composition by
maternal education. Does maternal education proxy for access to sex
selective technology, preferences for sons, etc.? In addition, how does
selection into the highest/lowest educated categories change over the 45
years of the study? How could this impact the interpretation of results?

[Response:]

[selection]

There are two possible explanations, economics and cultural.

For the economics one, the use of sex selection is mainly driven by the lower fertility
that comes from higher opportunity cost of time and the higher income that allow those
with higher education to use sex selection.
Here there is essentially no selection bias since the use of sex selection is driven
by factors that are identical across those with the same level of education.

The cultural explanation is that originally those with higher education where also those
groups with the strongest son preference (presumably those who are also higher caste).
The expansion of access to education brought other groups/castes into connection with
the higher castes and assimilation of their son preference norms.
Presumably the assimilation is not complete and those newer to higher education would
therefore have lower son preference and therefore lower use of sex selection.
This means that any appearance of lower use of sex selection could be a selection story,
and that the initial group's son preference is just as strong.

The cultural explanation also suggests a reason for why the states son preference 
appear to decline over time.
The ``newer'' entrants have lower initial son preference and therefore the average
son preference for high education women will decline over time.
\citep{bhat03}, \citep{pande07}.

@@

7. It is not clear why exactly 22, 23, 25 years are used a cut-off
points.

[Response:]
I have added a detailed discussion of recall error in the Appendices intended for online 
publication.
Furthermore, I have changed the cut-off to be 22 years of marriage or more for all surveys 
to simplify.
Even with the stricter cut-off there are still some evidence of recall error,
especially in region TK, where the sex ratio was substantially biased against females 
before sex selection became available.

8. I understand the empirical reason for not increasing the number of
variables. However, a key variable that is essential to consider is
region. This is important because regional influences on birth spacing
and sex selection are very strong as established in the literature. Sex
selection and abortion is especially strong in certain regions but not
in others. The regional differentials in fertility transition,
contraceptive use, spacing, sex ratios, abortions are clearly documented
in the literature. So it is vital to include this.

[Response:]
I agree completely that the regional differences in fertility, son preference, and use 
of sex selection are important.
To try to capture these differences, I have divided India into four broad regions 
depending on degree of son preference and initial fertility level as in 
\citet{retherford03b}, although expanded to include all states in the surveys.
In addition to the power problem, some education/region/spell/period combinations have too 
small sample sizes for the estimations to converge.
The lack of convergence is especially an issue for the middle-education group at the
higher spells.
I, therefore, first present the all-India results and then focus on regional differences
for only the most educated women, who are the main users of sex selection.

### 2019-03-11 response/response-demography-1.tex

5. The use of competing hazard models is not new in demographic research
and doesn’t require long exposition. This section can be cut
sustainably. I don’t think the methodological innovation is a key
contribution of the paper as the methods are established even if they
have not been used to examine spacing.

[Response:]

I have reduced the length of the section by more than 1/4 (the original section was 5
pages long, while the revised section is less than 3.5).
The first two paragraphs in the section now highlight how my approach is different from
prior research, especially the non-randomness of birth outcome and non-proportionality
assumption.

There are three important differences between my approach and what is standard
in the literature, and I believe further shortening would negatively impact readers'
ability to understand the results.
First, most research that use survival models employ proportional hazard models, so 
motivating and providing more information on the non-proportional set-up is important.
Second, the use of conditional survival curves is, to my knowledge, new, and, therefore,
requires a detailed discussion.
Third, the sex ratio calculations is a new way to use competing risk estimates and is 
required to understand the use of sex selection.

@@

It is also worthwhile to note that even some of the southern states appear to have
seen an increase in son preference over time, or, rather, daughter aversion
\citep{DiamondSmith2008}.

9. The three tables are logically organized and contain a wealth of
information. But there are too many comparisons to make in each of the
tables and I wonder if it would make sense to split the tables or
present some of the information in a much more reader friendly way (for
instance by using charts for some of the information).

[Response:]

Using graphs is an excellent suggestion.
Instead of the tables, I now show graphs for each of the education levels.
For each spell, I show the predicted average spacing, the predicted sex ratio, and the 
probability of having a birth by the end of the spell for each decade.
Including the probability of having a birth allows me to discuss the falling fertility 
more organically as requested by the editor.

The only downside is that I had to remove the confidence intervals for legibility. 
I, therefore, still include Tables 1-3, but have moved them to the Appendix, and I have 
added the probability of a birth to the tables.
I have also combined the 75th, 50th, and 25th percentiles results tables in the Appendix.

### 2019-03-11 paper/sex_selection_spacing-ver2.tex
Respond to R1's suggestion on results graphs
Discuss no education results

Women with no education follow a pattern consistent with son
preference with shorter spacing when they have only girls compared 
to when they have one or more sons, and the differences are often 
statistically significant as shown in Table \ref{tab:median_sex_ratio_low}.
Most of the women without education live in rural areas,
whereas there are relatively few urban women with no education.
There are especially very few urban women to based the third
and fourth spell results on, and I therefore focus on rural women.

Predicted median duration has increased over time within
each sex composition.
The exception is for the first spell, where there is little
change, and possibly even a small decline.

The differences in duration across sex compositions increase with 
spell number.
For the second spell, the difference in median duration between
having a girl or a boy as the first-born are mostly between a half
and one month.
For the third spell, the difference in duration between only girls 
and only boys is, on average, slightly over one month and statistically 
significant in all periods.
The differences for the fourth spell are between two and three months, 
except for the 1972--1984 period, which is also the only period where 
the difference is not statistically significant.

There are no clear time trends in the differences in median duration
across sex compositions or the predicted sex ratios across the four periods.
Despite that some sex ratios are statistically significantly higher 
than the natural sex ratio there is therefore little consistent evidence 
for the use of sex selection for women without education.
There has, for example, been relatively little change in the length
of spacing for rural women with two girls in the third spell and 
the predicted sex ratio was higher in the 1985--1994 period
than in the 2005--2016 period.
The possible exception is the fourth spell, where both duration 
and sex ratio has increased for women with three girls, although
the \emph{difference} across sex compositions has remained almost
the same.

@@

Women with one to seven years of education follow a pattern
broadly similar to those with no education as 
Table \ref{tab:median_sex_ratio_med} shows.
The sample size is more evenly distributed across urban and rural 
for this education group than for the no education women.
As a result, the only spells where there are few women to base 
results on are for the fourth spell for urban women and the first 
period of the fourth spell for rural women.

@@

\section{Additional Duration Results}

>>>>

The previous literature finds that women with no education are the least likely to use 
sex selection, which suggests that they would instead follow a traditional strategy to son 
preference with higher fertility and shorter birth intervals the fewer sons they have.
This pattern is supported by Figure \ref{fig:bootstrap_low}, but with important
differences across spells.
Most of the women without education live in rural areas, and I therefore focus on rural 
women.

The initial high fertility of women with no education shows clearly in the results.
In the 1972--1984 period almost all women had at least four children, irrespectively
of the sex composition of the children.
Over time, however, the likelihood of having a third or fourth child decreased for women 
with at least one son, and more so the more sons they had.
Hence, fertility have begun to fall even among women with no education, as long as they 
have at least one son.
Two additional fertility trends stand out.
First, essentially all women still have a second birth, whether the first child was
a boy or a girl.
Second, for women with only girls there is almost no reduction in the probability of 
having a birth across time and across spells.

Birth intervals have increased in length over time, although the increases are not
uniform over spells and sex compositions of prior children.
The smallest increases have been for the second spell, with most increases between one
and two months.
Interestingly, son preference appear to have little effect on spacing for the second
spell, with very small, albeit statistically significant, differences in birth intervals 
depending on the sex of the first child.
This small difference is in line with the high likelihood of having a second child.
The second spell also shows convergence in birth intervals, especially in the urban
areas where the predicted average duration is now the same whether the first child was
a boy or a girl.

Where son preference in birth intervals shows most clearly is for the fourth spell.
Despite the increase in spacing even for those with three girls, the increases in 
spacing have been substantially larger for families with at least one son.
As for fertility, the differences are larger the more sons a family has.

Despite the general finding that use of sex selection is confined to higher education
women, the predicted sex ratios for those with only girls is statistically significantly
higher than the natural ratio for the third and fourth spell.
Hence, it is possible that at least part of the increased  birth intervals for those
with only girls comes from the use of sex selection and that the differences in
birth spacing across sex compositions would be even larger in the absense of sex selection.

@@

Women with one to seven years of education follow a pattern
broadly similar to those with no education as 
Figure \ref{fig:bootstrap_med} shows.
The sample size is more evenly distributed across urban and rural 
for this education group than for the no education women.
As a result, the only spells where there are few women to base 
results on are for the fourth spell for urban women and the first 
period of the fourth spell for rural women.

@@

\section{Duration Results Tables}
